---
title: "Final Project"
output:
  html_document: default
  pdf_document: default
date: '2022-05-17'
editor_options:
  markdown:
    wrap: sentence
---

First, lets import the relevant libraries:

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library (ggplot2)
library (readr)
library(dplyr)
library(matrixStats)
```

Loading our data from a csv file:

```{r}
raw_data <- readr::read_csv("https://raw.githubusercontent.com/YuvalRubinstein99/Data_Analytics_Course/main/The_Chase__Dataset.csv")
```

Lets get to know our data better:

```{r}
glimpse(raw_data)
```

Since that the dataset is built in a horizental structure, we are going to add a few columns that would help us treat each row as a specific group:

*group_id - int type, will hold a unique ID for each group.* fast_round_sum - dbl type, will hold the initial sum of the fast round for the entire group.
*team_members_left - dbl type, will hold the amount of team members that made it to the last stage.* drop_outs - dbl type, will hold the maount of team members that didn't make it to the last stage.
*avg_age - dbl type, will hold the average age of the entire group.* std_age - dbl type, will hold the std of the age of the entire group.

```{r}
fast_rounds = c("p_1_fast_round_sum", "p_2_fast_round_sum", "p_3_fast_round_sum","p_4_fast_round_sum")

player_stat = c("p1_round_status", "p_2_round_status", "p_3_round_status", "p_4_round_status")

player_age = c("p_1_age","p_2_age","p_3_age","p_4_age")
p1_risk_cols = c("p_1_play_sum_chosen","p_1_fast_round_sum")
p2_risk_cols = c("p_2_fast_round_sum", "p_2_play_sum_chosen") 
p3_risk_cols = c("p_3_fast_round_sum", "p_3_play_sum_chosen") 
p4_risk_cols = c("p_4_fast_round_sum", "p_4_play_sum_chosen") 
chaser <- raw_data %>%
  mutate(group_id = row_number()) %>%
  mutate(fast_round_sum = rowSums(chaser[, fast_rounds])) %>% 
  mutate(team_members_left = rowSums(chaser[, player_stat])) %>%
  mutate(drop_outs = 4 - team_members_left) %>%
  mutate(avg_age = rowMeans(chaser[, player_age])) %>%
  mutate(age_std = rowSds(as.matrix(chaser[, player_age]))) %>%
  mutate(p1_risk_taker = rowDiffs(as.matrix(chaser[,p1_risk_cols])) > 0) %>%
  mutate(p2_risk_taker = rowDiffs(as.matrix(chaser[, p2_risk_cols])) > 0) %>%
  mutate(p3_risk_taker = rowDiffs(as.matrix(chaser[, p3_risk_cols])) > 0) %>%
  mutate(p4_risk_taker = rowDiffs(as.matrix(chaser[, p4_risk_cols])) > 0) 

chaser

```

Lets check our new data variables:

```{r}
summary(chaser)
```

Now we'll check the different distributions of our variablesת Lets start with the right answers distribution:

```{r}

questions_dist <- ggplot(chaser, aes(x=question_answered)) +
  geom_histogram(bins=20, fill="darkolivegreen1")

questions_dist

```

Lets see the age distribution:

```{r}
ggplot(data=chaser, aes(x=avg_age))+
  geom_density(fill="darkolivegreen1")
```

Lets check the connection between the average group age to the group total sum of money:

```{r}
ggplot(data = chaser, aes(x = avg_age, y = team_total_sum,
color = '')) + geom_point()

```


now we gonna check distributions of risk takers while:
1 represents if the player was willing to take the 
```{r risk taking}

```
\`\`\`
