---
title: "Final Project"
output:
  html_document: default
  pdf_document: default
date: '2022-05-17'
editor_options:
  markdown:
    wrap: sentence
---

First, lets import the relevant libraries:

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library (ggplot2)
library (readr)
library(dplyr)
library(matrixStats)
library(grid)
library(gridExtra)
```

Loading our data from a csv file:

```{r}
raw_data <- readr::read_csv("https://raw.githubusercontent.com/YuvalRubinstein99/Data_Analytics_Course/main/The_Chase__Dataset.csv")
```

Lets get to know our data better:

```{r}
glimpse(raw_data)
```

Since that the dataset is built in a horizental structure, we are going to create 4 tables - one for each player and combine it all to a one vertical table: 

```{r}
# Adding a group id number:
raw_data <- raw_data %>%
  mutate(group_id = row_number())

# Creating tables for each player:
p1_tb <- raw_data %>%
  select(p_1_gender, p_1_age, p_1_fast_round_sum, p_1_play_sum_chosen, p1_round_status, group_id, team_total_sum, question_answered, game_result, season) %>%
   rename(
    Gender = p_1_gender,
    Age = p_1_age,
    Fast_round_sum = p_1_fast_round_sum,
    Play_sum_chosen = p_1_play_sum_chosen,
    Round_status = p1_round_status,
    Team_question_answered = question_answered
    )

p2_tb <- raw_data %>%
  select(p_2_gender, p_2_age, p_2_fast_round_sum, p_2_play_sum_chosen, p_2_round_status, group_id, team_total_sum, question_answered, game_result, season) %>%
     rename(
    Gender = p_2_gender,
    Age = p_2_age,
    Fast_round_sum = p_2_fast_round_sum,
    Play_sum_chosen = p_2_play_sum_chosen,
    Round_status = p_2_round_status,
    Team_question_answered = question_answered
    )

p3_tb <- raw_data %>%
  select(p_3_gender, p_3_age, p_3_fast_round_sum, p_3_play_sum_chosen, p_3_round_status, group_id, team_total_sum, question_answered, game_result, season) %>%
     rename(
    Age = p_3_age,
    Gender = p_3_gender,
    Fast_round_sum = p_3_fast_round_sum,
    Play_sum_chosen = p_3_play_sum_chosen,
    Round_status = p_3_round_status,
    Team_question_answered = question_answered
    )

p4_tb <- raw_data %>%
  select(p_4_gender, p_4_age, p_4_fast_round_sum, p_4_play_sum_chosen, p_4_round_status, group_id, team_total_sum, question_answered, game_result, season) %>%
     rename(
    Gender = p_4_gender,
    Age = p_4_age,
    Fast_round_sum = p_4_fast_round_sum,
    Play_sum_chosen = p_4_play_sum_chosen,
    Round_status = p_4_round_status,
    Team_question_answered = question_answered
    )

## Combine the 4 tables and creating a unique player id:
combined_data <-rbind(p1_tb, p2_tb, p3_tb, p4_tb)

glimpse(combined_data)

```

We are going to add a few columns:
* player_id - int type, holds a unique value for each player
* risk_taker - int type, holds 1 if the player took risk and 0 if not:

```{r}
risk_cols = c("Play_sum_chosen", "Fast_round_sum")

chaser <- combined_data %>%
  mutate(
    player_id = row_number(),
    risk_taker = ifelse(rowDiffs(as.matrix(chaser[ , risk_cols])) > 0, 1, 0))

```

Lets check our new data variables:

```{r}
summary(chaser)
```

Now we'll check the different distributions of our variablesת Lets start with the right answers distribution:

```{r}

questions_dist <- ggplot(chaser, aes(x=Team_question_answered)) +
  geom_histogram(bins=20, fill="darkolivegreen1")

questions_dist

```

Lets see the age distribution:

```{r}

ggplot(data=chaser, aes(x= Age)) +
  geom_density(fill="darkolivegreen1")


```

Lets check the connection between the average group age to the group total sum of money:

```{r}
ggplot(data = chaser, aes(x = Age, y = Fast_round_sum,
color = '')) + geom_point()


```

```{r}
#par(mfrow=c(2,2))

player_bp <- boxplot(Fast_round_sum ~ Gender,
data=chaser,
main=" Fast Round Sum by Gender",
col="orange",
border="gray"
)
```




now we gonna check distributions of risk takers while:
1 represents if the player was willing to take the risk
```{r}

ggplot(chaser, aes(x = count(as.vector(chaser[,c("game_result")] == 0)), y = sum_risktakers)) + theme_bw() +
  stat_smooth(method = "lm") + geom_point()

risktakers <- select(chaser, sum_risktakers, game_result, team_total_sum)
ggplot(risktakers, aes( y = sum_risktakers,x = team_total_sum)) + theme_bw() +
  stat_smooth(method = "lm") + geom_point()

risk_taking_players <- select(chaser,
                              group_id,
                              p1_risk_taker,
                              p2_risk_taker,
                              p3_risk_taker,
                              p4_risk_taker) %>%
  pivot_longer(., 
               cols = c(p1_risk_taker,
                        p2_risk_taker,
                        p3_risk_taker,
                        p4_risk_taker),
               names_to = "player",
               values_to = "is_risk_taker") %>%
  mutate(num_player = ifelse(player == "p1_risk_taker", 1,
         ifelse(player == "p2_risk_taker", 2,
         ifelse(player == "p3_risk_taker",3 ,4)))) %>%
  select(num_player, is_risk_taker) %>%
  group_by(num_player) %>%
  filter(is_risk_taker == 1) %>%
  summarise(num_player = n)

```


